Interactive Visualization of Hierarchically Structured Data

### 2017-02-15 treelapse.Rmd
Add iris figure

```{r iristimebox, fig.cap = "A toy application to the Iris data gives an example of how linking in treelapse can be applied to combine hierarchical clustering and parallel coordinates views."}
include_graphics("iris_timebox.pdf")
```

>>>>

```{r iristimebox, fig.cap = "A toy application to the Iris data gives an example of how linking in treelapse can be applied to combine hierarchical clustering and parallel coordinates views."}
include_graphics("figure/iris_timebox.pdf")
```
